Thesis Title

### 2022-11-02 titlepage.tex
Update with basic structure
update
start resumo

        {\includegraphics{figures/cover/UL+FMUL-VerticalPositivo.png}}

        \vspace{0.5cm}

        \Huge
        {Towards accreditation in metagenomics \\[1ex] for clinical microbiology}
        \normalsize

        \vspace{0.5cm}

        Catarina Inês Marques de Sousa Mendes

        \vspace{0.5cm}

@@

        \vspace{0.5cm}

@@

        \vspace{0.5cm}

        Fundação para a Ciência e Tecnologia SFRH/BD/129483/2017

        \vspace{0.5cm}

>>>>

        \vspace{1cm}

        {\includegraphics{figures/cover/UL-VerticalPositivo.png}}

        \vspace{1cm}

        \huge
        \textbf{Towards accreditation in metagenomics \\[1ex] for clinical microbiology}
        \normalsize

        \vspace{1cm}

        \large
        Catarina Inês Marques de Sousa Mendes
        \normalsize

        \vspace{1cm}

@@

        \vfill

@@

        \vspace{0.8cm}
